---
  layout: post
  leafletmap: true
  always_allow_html: yes
  output: github_document
---
  landusepl
======

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

Display, convert and export CORINE Land Cover - CLC 2018 map to WAsP (Wind Atlas Analysis and Application Program) roughness file for a selected county in Poland.

### CORINE Land Cover - CLC 2018 for Poland
Description of the project is available on the web page <https://clc.gios.gov.pl/index.php/clc-2018/o-projekcie> where data can be requested.

### Obligatory information due to the use of CORINE Land Cover - CLC 2018

**Acording to the terms of use, please find the below obligatory statement:**

*„Projekt Corine Land Cover 2018 w Polsce został zrealizowany przez Instytut Geodezji i Kartografii i sfinansowany ze środków Unii Europejskiej. Wyniki porojektu zostały pozyskane ze strony internetowej Głównego Inspektoratu Ochrony Środowiska <https://clc.gios.gov.pl>.*

### Change and processing of CORINE Land Cover - CLC 2018 data set

The package landusepl uses the main CORINE Land Cover - CLC 2018 map file divided into voivodeships. Due to this conversion it in the below voivodeships of Poland data were lost:

* TERYT code 12, Lesser Poland, województwo małopolskie
* TERYT code 20, Podlaskie, województwo podlaskie
* TERYT code 22, Pomeranian, województwo pomorskie
* TERYT code 24, Silesian, województwo śląskie
* TERYT code 26, Holy Cross, województwo świetokrzyskie
* TERYT code 30, Greater Poland, województwo wielkopolskie

### Installation

Get the development version 0.0.0.9100 from github:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("prcwiek/landusepl")
```

### Use

```{r}
library(landusepl)
```

For example, let's take a look at Zachodniopomorskie voivodeship (district) in Poland. 
First we have to find a county for which we want to generate maps. We have to do it with TERYT codes and found code_je for a county we are 
interested in. 

TERYT is a code of voivodeship. The complete list of voivodeships in Poland is presented below.

```{r}
library(dplyr)
show_teryt() %>% select(TERYT, Voivodeship) %>% distinct(TERYT, Voivodeship) %>% arrange(Voivodeship)
```


Let's find all counties in Zachodniopomorskie voivodeship (district) which has TERYT code 32. The code_je is a code of a county consists of TERYT + 2 digits identifier.
```{r}
show_teryt(teryt = "32") %>% print(n = Inf)
```

Let's take a look at the borders of Gryfinski County, which has a code_je 3206

```{r eval = FALSE}
county_map(code_je = "3206")
```

And its land cover according to CORINE Land Cover - CLC 2018 for Poland. 

```{r eval = FALSE}
corine_map(code_je = "3206")
```

In the above map for each area there are two values displayed, the CODE_18 and roughness length assigned according to the below table.

```{r}
show_clc()
```

It is possible to export the above table as csv file, modify and upload it back.

```{r eval = FALSE}
# save with the assignation table to a file, .csv is added fname automatically
save_clc(fname = "assignation_table")

# load a file with the assignation table
load_clc(fname = "assignation_table.csv")
```

The export to a WAsP map file (https://www.wasp.dk/Support/FAQ#maps__roughnessandorography)
```{r eval = FALSE}
export_wasp_map(fname = "gryfinski.map", code_je = "3206", wgs_zone = 33, buffer = -1)
```
It is necessary to provide the correct UTM WGS34 zone, for Poland 33 or 34. 
The buffer has to be negative and will be used to shrink all areas. The roughness between areas will be equal to 0.03. The default value is -1 m. 
